---
title: "Assignment B-4 Option A: Strings and/or Functional Programming"
output: github_document
---

1. Install the required package

<!-- -->

    install.packages("palmerpenguins")
    install.packages("tidytext")
    install.packages("ggwordcloud")

1.  Load the packages below.

```{r}
library(janeaustenr)
library(tidytext)
library(tidyverse)
library(ggwordcloud)
library(testthat)
```

2. Exercise 1: Remove “stop words” and make a plot of the most common words in the book (Pride & Prejudice from janeaustenr).

# To understand the structure of the austen_books
```{r}
print(austen_books()) # print the header and first 10 rows of austen_books() 
```

# Set up the data as we needed
```{r}
words_in_prideprejudice <- austen_books() %>%
  unnest_tokens(word, text) %>% # split text into tokens(words)
  filter(book == "Pride & Prejudice") %>% # select the book Pride & Prejudice
  count(word, sort = TRUE) %>% # count the number of each word in the book Pride & Prejudice
  anti_join(stop_words, by = "word") # remove stop words
words_in_prideprejudice
```

# Get the most common words for bar plot
```{r}
common_words_for_bar <- words_in_prideprejudice %>%
  # I choose less common words for bar plot, otherwise the plot will be messy
  filter(n > 100) # get the words whose number exceeds 100
common_words_for_bar
```

# Draw a bar plot for the most common words in Pride & Prejudice
```{r}
common_word_plot <- ggplot(common_words_for_bar, aes(x = word, y = n)) + # ggplot where x = word, y = n
  geom_bar(stat="identity") + # draw bar plot 
  labs(x = "Word", y = "Number of the word", title = "Distribution of the most common word")
common_word_plot + coord_flip()
```

```{r}
common_words_for_cloud <- words_in_prideprejudice %>%
  filter(n > 50) # get the words whose number exceeds 100
common_words_for_cloud
```

# Draw a word cloud for the most common words in Pride & Prejudice
```{r}
ggplot(common_words_for_cloud, aes(label = word, size = n, 
                                   color = factor(sample.int(20, nrow(common_words_for_cloud), replace = TRUE)))) +
  geom_text_wordcloud(shape = "circle") +
  scale_size_area(max_size = 10) + 
  theme_minimal() 
```

3. Exercise 2: Make a function that converts words to your own version of Pig Latin.

```{r}
#' Convert Words to My Pig Latin Version
#'
#' The function can convert words to my version of Pig Latin
#' For words that end with consonant sounds, all letters after the last vowel are placed at the beginning of the word sequence.
#' When words end with consonant clusters (multiple consonants that form one sound), the whole sound is added to the beginning.
#' For words end with vowel sounds, one moves the last vowel(s) along with the consonant clusters to the beginning. 
#' If the penultimate character is also a vowel, only the last vowel is moved.
#' Add “wow” to the end of the word
#'
#' @param words - An English string that you want to transfer to the Pig Latin version 
#' 
#' @return A string that in my Pig Latin version (all words will be in the lowercase)
#' 
#' @examples
#' pig_latin("Example")
#' pig_latin("Chenru Zhao")
#' pig_latin("this is a example")

pig_latin <- function(words) {
  if(!assertthat::is.string(words)) {
    stop("The input should be a string.")
  }
  
  if(words == "") {
    stop("The input is empty.")
  }
  
  vowel_sounds <- c("a", "e", "i", "o", "u")
  is_vowel_sound <- function(c) {
    c %in% c(vowel_sounds, toupper(vowel_sounds))
  }
  
  get_last_vowel_index <- function(word) {
    char_list <- stringr::str_split(word, "")[[1]]
    purrr::detect_index(char_list, is_vowel_sound, .dir = "backward")
  }
  
  words_list <- strsplit(words, "\\s+")
  pig_lation_result <- ""
  for(word in words_list[[1]]) {
    word <- tolower(word)
    word_count <- nchar(word)
    last_vowel_index <- get_last_vowel_index(word)
    if(last_vowel_index == word_count && last_vowel_index != 1) {
      word <- paste((str_sub(word, word_count, word_count)), (str_sub(word, 1, word_count-1)), sep = "")
      last_vowel_index <- get_last_vowel_index(word)
    }
    pig_latin_word <- paste((str_sub(word, last_vowel_index+1)), (str_sub(word, 1, last_vowel_index)), "wow", sep = "")
    if(pig_lation_result == "") {
      pig_lation_result <- paste(pig_lation_result, pig_latin_word, sep = "")
    } else {
      pig_lation_result <- paste(pig_lation_result, pig_latin_word)
    }
  }
  
  return(pig_lation_result)
}
```

```{r}
vowel_sounds <- c("a", "e", "i", "o", "u")
  is_vowel_sound <- function(c) {
    c %in% c(vowel_sounds)
  }
  
  get_last_vowel_index <- function(word) {
    char_list <- stringr::str_split(word, "")[[1]]
    #print(char_list)
    purrr::detect_index(char_list, is_vowel_sound, .dir = "backward")
  }
  
  words_list <- stringr::str_split("test  pie receive", "\\s+")
  pig_lation_result <- ""
  for(word in words_list[[1]]) {
    word_count <- nchar(word)
    word <- tolower(word)
    #char_list <- stringr::str_split(word, "")[[1]]
    last_vowel_index <- get_last_vowel_index(word)
    #print(last_vowel_index)
    if(last_vowel_index == word_count && last_vowel_index != 1) {
      #print(word)
      word <- paste((str_sub(word, word_count, word_count)), (str_sub(word, 1, word_count-1)), sep = "")
      #print(word)
      last_vowel_index <- get_last_vowel_index(word)
      #print(last_vowel_index)
    }
    pig_latin_word <- paste((str_sub(word, last_vowel_index+1)), (str_sub(word, 1, last_vowel_index)), "wow", sep = "")
    #print(pig_latin_word)
    if(pig_lation_result == "") {
      pig_lation_result <- paste(pig_lation_result, pig_latin_word, sep = "")
    } else {
      pig_lation_result <- paste(pig_lation_result, pig_latin_word)
    }
    #print(pig_lation_result)
  }
  print("result")
  print(pig_lation_result)
```

# Examples of my pig_latin function
```{r}
result1 <- pig_latin("Example")
print(result1)
```

```{r}
result2 <- pig_latin("Chenru Zhao")
print(result2)
```

```{r}
result3 <- pig_latin("This is a example")
print(result3)
```

# Test
```{r}
test_that("pig_latin works", {
  # 
  expect_equal(pig_latin("I receive a pie"), "iwow vereceiwow awow epiwow")
  # 
  expect_equal(pig_latin("happy"), "ppyhawow")
  # 
  expect_equal(pig_latin("hey"), "yhewow")
  #
  expect_error(pig_latin(c(1,2,3,4,5)))
  # 
  expect_error(pig_latin(""))
}) 
```